MSc Background Report

### 2019-06-03 Report/Progress_Report/Background.tex
mostly config

\documentclass[12pt]{article}

\usepackage{indentfirst}
\usepackage{geometry}
 \geometry
 {
     a4paper,
     left=25mm,
     right=25mm,
     top=25mm,
     bottom=25mm,
 }

@@

\section{Introduction}

@@

Current methods of visual speech prediction, often referred to as lip reading, focuses on training machine learning models on 2D temporal data of participants speaking, labelled with the accompanying spoken text \cite{Chung2016}, \cite{Assael2016}, \cite{Chung2017}, \cite{Shillingford2018}.
However there has been little progress in lip reading from 3D temporal models which contain depth information of the subject.
A substantial barrier to this problem is the lack of 3D datasets of subjects speaking when compared to the relative abundance of video datasets.
To first attempt this problem, new datasets which capture 3D temporal models of subjects heads speaking must be established by the community.

\section{Lip Reading}
In recent years the problem of Lip Reading has seen huge advances due to the availability of new datasets and the use of Deep Learning models.
In 2016 the Lip Reading Words (LRW) dataset was published \cite{Chung2016}, followed by Lip Reading Sentences (LRS) in 2017 \cite{Chung2017} and later Large-Scale Visual Speech Recognition (LSVSR) in 2018 \cite{Shillingford2018}, each of which larger in size and resulted in a model which outperforms previous models.
Chung et al \cite{Chung2016} used a convolutional model based on the VGG-M architecture which produced character level distributions with the LRW dataset, these distributions are then processed by a language model for text prediction.
The LRW dataset contains over 1000 hours of spoken text taken from BBC broadcasts, with a over 1000 different speakers, variations in angles and lighting, a vocabulary size of over 1000 words and over one million word utterances.

@@

\section{Data Generation}
\subsection{Data Capture}
\begin{itemize}
    \item 2D datasets
    \item 3D datasets
    \item Capture New Dataset
\end{itemize}

\subsection{Statistical Models}
\begin{itemize}
    \item Audio driven models
\end{itemize}

\subsection{Generative Models}
\begin{itemize}
    \item Intro to GANs
    \item Issues with GANs
    \item Progression of GANs
    \item GANs for synthesising 2D lip sync video
\end{itemize}

\section{3D Modelling}
\begin{itemize}
    \item blendshapes
    \item Model Correspondence
\end{itemize}

\section{Recurrent Models}
\begin{itemize}
    \item Recurrent networks
    \item LSTMs
    \item Attention Mechanism
\end{itemize}

\section{Speech Recognition}
Deep Speech \cite{Karras2017a}

\section{Current Work and Future Work}
Data collection

>>>>

\documentclass[12pt]{report}

\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage{indentfirst}
\usepackage{geometry}
 \geometry
 {
     a4paper,
     left=25mm,
     right=25mm,
     top=25mm,
     bottom=25mm,
 }

@@

\chapter{Introduction}

@@

Current methods of visual speech prediction, often referred to as lip reading, focuses on training machine learning models on 2D temporal data of participants speaking, labelled with the accompanying spoken text \cite{Chung2016, Assael2016, Chung2017, Shillingford2018}.
However there has been little progress in lip reading from 3D temporal models which contain depth information of the subject.
A substantial barrier to this problem is the lack of 3D datasets of subjects speaking when compared to the relative abundance of video datasets.
To first attempt this problem, new datasets which capture 3D temporal models of subjects heads speaking must be established by the community.

\chapter{Lip Reading}
In recent years the problem of Lip Reading has seen huge advances due to the availability of new datasets and the use of Deep Learning models.
In 2016 the Lip Reading Words (LRW) dataset was published \cite{Chung2016}, followed by Lip Reading Sentences (LRS) in 2017 \cite{Chung2017} and later Large-Scale Visual Speech Recognition (LSVSR) in 2018 \cite{Shillingford2018}, each of which larger in size and resulted in a model which outperforms previous models.
Chung et al \cite{Chung2016} used a convolutional model based on the VGG-M architecture which produced character level distributions with the LRW dataset, these distributions are then processed by a language model for text prediction.
The LRW dataset contains over 1000 hours of spoken text taken from BBC broadcasts, with a over 1000 different speakers, variations in angles and lighting, a vocabulary size of over 1000 words and over one million word utterances.

@@

\chapter{Data Generation}
\section{Data Capture}
Current lip reading models currently make use of 2D temporal data such as videos.
This is convenient as video data is already widely available and relatively straightforward to process.
The reason for the wide availability of video data is due to the ease of capturing and viewing such data.
Unlike 2D temporal data, 3D temporal data or 3D video, requires multiple cameras to record simultaneously, which requires synchronisation, adding to the complexity of the system.
The data must then be processed to produce the final product, whether this is in the form of video with depth information or more complex 3D scans \cite{Li2017}.

\subsection{2D Datasets}
Due to the large availability of video data, datasets such as LRW, LRS and LSVSR have been constructed by compiling the appropriate data.
LRW and LRS are both comprised of content from BBC broadcasts \cite{Chung2016, Chung2017}

\subsection{3D Datasets}

\subsection{Original Dataset}

\section{Statistical Models}
\begin{itemize}
    \item Audio driven models
\end{itemize}

\section{Generative Models}
\begin{itemize}
    \item Intro to GANs
    \item Issues with GANs
    \item Progression of GANs
    \item GANs for synthesising 2D lip sync video
\end{itemize}

\chapter{3D Modelling}
\begin{itemize}
    \item blendshapes
    \item Model Correspondence
\end{itemize}

\chapter{Recurrent Models}
\begin{itemize}
    \item Recurrent networks
    \item LSTMs
    \item Attention Mechanism
\end{itemize}

\chapter{Speech Recognition}
Deep Speech \cite{Karras2017a}

\chapter{Current Work and Future Work}
Data collection
